\documentclass[11pt]{article}

% ---------- Packages ----------
\usepackage[margin=0.75in]{geometry}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[hidelinks]{hyperref}
\raggedright%
\setlength{\emergencystretch}{2em}

% ---------- Colors ----------
\definecolor{primary}{HTML}{5B8DEF} % soft blue
\definecolor{muted}{HTML}{777777}

% ---------- Section Style ----------
\titleformat{\section}
  {\large\bfseries}
  {}
  {0pt}
  {}
  [\titlerule]

\titlespacing{\section}{0pt}{10pt}{6pt}

% ---------- Lists ----------
\setlist[itemize]{leftmargin=*, noitemsep}

% ---------- Document ----------
\begin{document}

% ---------- Header ----------
{\color{primary}\Huge \textbf{Christopher Peterson}} \\[-2pt]

\vspace{6pt}

\small
\faEnvelope\ \href{mailto:chris.will.peterson@gmail.com}{chris.will.peterson@gmail.com} \quad
\faLinkedin\ \href{https://www.linkedin.com/in/chriswillpeterson/}{chriswillpeterson} \quad
\faGithub\ \href{https://github.com/ptechr}{ptechr} \quad
\faMapMarker* \ Redlands, CA

\vspace{14pt}

% ---------- Summary ----------
\section{Summary}

\vspace{6pt}

Business Intelligence Engineer with 7+ years of experience translating large-scale operational 
data into actionable insights and scalable analytics systems at Amazon. Designed real-time data 
platforms, automated ETL pipelines, and forecasting models supporting \$1B+ business decisions 
and 165+ stakeholder teams. Combines strong data engineering fundamentals 
(Spark, SQL, AWS, distributed systems) with advanced statistical modeling and stakeholder-facing 
tools to deliver measurable outcomes.

% ---------- Experience ----------
\section{Experience}

\vspace{6pt}

\textbf{Senior Business Intelligence Engineer} \\
{\color{primary}Amazon}

\small
\faCalendar\ July 2024 -- Present \quad
\faMapMarker* \ Virtual Location California (Remote)
\normalsize

\begin{itemize}[itemsep=4pt]

  \item Designed and scaled a real-time distributed data ingestion platform processing
1.3B+ events per day with zero data loss, reducing inventory data latency from
24 hours to 10 minutes through a hand-crafted ETL pipeline using SNS, SQS, ECS, Kinesis, 
DynamoDB, \& S3.

  \item Scaled team-owned Parquet-based data lake by replacing legacy snapshot pipelines with 
  fully stream-derived datasets featuring optimized partitioning, deduplication, enrichment, and 
  schema design—eliminating race conditions, boosting query performance, and driving adoption to 
  178 production tables (4,350\% growth from 2024), generating 1,200 access requests across 165 teams in 2025.

  \item Developed a Spark-based distributed life-cycle engine processing 900M records/day, constructing 
  end-to-end item lineage with deterministic hashing and FIFO-based indexing using a dual-tiered maximum 
  bi-partite matching algorithm. This generated life-cycle completeness to 97.8\% and reduced lineage computation 
  from multiple weeks of developer effort to minutes, enabling scalable inventory tracing across Amazon as a generalized 
  inventory-tracing-as-a-service model.

  \item Translated life-cycle and defect prediction signals into data-driven operational 
  decisions using automated validation, confidence-interval sampling, and prioritization logic. 
  Delivered \$21.8M in realized savings in 2025 (\$34M annualized) and improved network defect 
  remediation efficiency by 334\%, validating model-driven interventions.

  \item Implemented CI/CD governance and version-controlled deployments for over 1,700 production data pipelines, 
  enforcing code review verification and locked UI edits. Reduced deployment risk and improved reliability across a 
  highly interdependent data ecosystem serving hundreds of teams.

\end{itemize}

\vspace{6pt}

\textbf{Business Analyst} \\
{\color{primary}Amazon}

\small
\faCalendar\ March 2022 -- July 2024 \quad
\faMapMarker* \ Virtual Location California (Remote)
\normalsize

\begin{itemize}[itemsep=4pt]

  \item Built and deployed a North America inventory labor forecasting system managing a \$1.3B budget, delivering 
  2.8M metric forecasts across 320 fulfillment centers over a 104-week horizon. Engineered fully automated ETL pipelines 
  for 22k KPIs and designed dynamic Sagemaker time series models supporting multiple prediction types (Linear Regression, 
  SARIMAX, KNN, Random Forest, XGBoost) with hierarchical reconciliation, hyperparameter optimization, and residual course 
  correction. Developed custom EDA and visualization notebooks analyzing seasonality, correlations, and network-FC dynamics. 
  Delivered a stakeholder-facing labor planning web portal with override capabilities, algebraic optimization recalculation, and network-level 
  reporting, enabling actionable, constraint-aware workforce planning.

  \item Delivered a rapid-response tooling solution that eliminated schema deployment friction in Amazon’s 
  centralized data lake, which automated transformation from Redshift to SDL schemas with full support for 
  constraint keying and data type translations. This reduced dataset onboarding time 6× and scaled organically to 
  2,000+ engineers across the Software Development, Data Engineering, Business Intelligence, and Data Science job families. 

\end{itemize}

\vspace{6pt}

\textbf{Data Analyst} \\
{\color{primary}Amazon}

\small
\faCalendar\ August 2018 -- March 2022 \quad
\faMapMarker* \ Redlands, CA
\normalsize

\begin{itemize}[itemsep=4pt]
  \item Built a quarterly logistic regression model to detect shift false pick shorts in real time, achieving 79\% precision 
  and enabling targeted coaching. Drove site to become the top-performing building in the region for pick short DPMO 
  for all of Q4 2021.

  \item Developed a supervised multinomial classification model to identify root cause work reasons and associate responsibility 
  for bin inventory adjustments, increasing regional classification accuracy from 3.5\% (manual) to 52\% via automated workflow.

  \item Designed a bias-free quality coaching application that measures pre- and post-coaching performance, enabling data-driven 
  manager-associate conversations. In 2021, 75.6\% of coachings led to improvement, with median DPMO reductions of 49.55\%.
\end{itemize}

% ---------- Skills ----------
\section{Skills}

\vspace{6pt}

\begin{itemize}[itemsep=4pt]
  \item \textbf{Programming/Scripting}: Python, TypeScript, HTML, CSS
  \item \textbf{Version Control}: Git, ECR, Docker
  \item \textbf{Infrastructure as Code (IaC)}: AWS CDK
  \item \textbf{Data Engineering/ETL}: PySpark, SQL, SQS, SNS, Kinesis, DynamoDB, 
  Lambda, S3, ECS, Redshift, EMR, Partition Optimization, Schema Design
  \item \textbf{Statistics/Model Selection}: VIF, AIC/BIC, Adjusted R-Squared, SHAP, PCA, 
  Confidence Intervals, Hypothesis Testing, Paired t-tests, A/B Pilot Selection/Validation, Autocorrelation, 
  Correlation, Probability Theory, Combinatorics, Augmented Dickey-Fuller Test, Data Interpolation, 
  Hyperparameter Grid Searching, Recursive Feature Elimination, Train/Test Splits
  \item \textbf{Predictive Modeling}: Sagemaker, Timeseries, Sklearn, Statsmodels, PyTorch, SARIMAX, XGBoost, Random 
  Forest Regression, Linear Regression, Logistic Regression, Lasso Regression, K-nearest Neighbor, Artificial Neural Network
  \item \textbf{Visualization}: Quicksight, Matplotlib, AG Charts, Jupyter Notebook
\end{itemize}

% ---------- Education ----------
\section{Education}
\vspace{6pt}

\textbf{Bachelor's of Business Administration, Business Management (BBA)} \\
{\color{primary}Marywood University}

\small
\faCalendar\ 2012 -- 2015 \quad
\faMapMarker* \ Scranton, PA
\normalsize

\begin{itemize}

  \item Placed 2\textsuperscript{nd} in Business Accreditation Assessment
  \item 3.76 Business GPA
  \item Dean's List Recognition
  \item NCAA Baseball Player

\end{itemize}

\end{document}